---
title: 'Question #2'
author: ""
date: ""
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::knit_hooks$set(crop = knitr::hook_pdfcrop)
```

$$\\[.01in]$$

# *Calculate measures of centrality and similarity in networks depending on the type of tie? Which tie type generates the most similar network in terms of introversion? Which tie type is the most dissimilar?*


$$\\[.01in]$$



#### ***Tie Types***
  + **Tie Type 1** = I have texted in the last 7 days
  + **Tie Type 2** = I have met during my time in MBDS
  + **Tie Type 3** = Is my friend
  + **Tie Type 4** = I ask for advice/help
  + **Tie Type 5** = Asks me for help/advice


$$\\[.01in]$$



```{r, include=FALSE}
## Set-up
library(tidyverse)
library(lubridate)
library(dplyr)
library(ggplot2)
library(sna)
library(readxl)
library(network)
library(splitstackshape)
library(igraph)
setwd("~/Desktop/BDS516")
edge_list <- read_csv("edge_list.csv")
edge_list <- edge_list %>% select(-X1)
node_list <- read_csv("node_list.csv")
node_list <- node_list %>% select(-X1)
```


### **Calculating Measures**

```{r}
node_clean <- node_list
node_clean[is.na(node_clean)] <- -1
```


###### Calculating measures of centrality and similarity in networks for **Tie Type 1**

```{r, message=FALSE, warning=FALSE}
edge1 <- edge_list %>% filter(Tie_Type == 1)
net1 <- graph_from_data_frame(d = edge1, vertices = node_clean, directed = TRUE)

deg1 <- degree(net1, mode="all") ## Degree
avg_deg1 <- mean(deg1)

close1 <- closeness(net1, mode="all", weights=NA) ## Closeness
avg_close1 <- mean(close1)

between1 <- betweenness(net1, directed=T, weights=NA) ## Betweenness
avg_between1 <- mean(between1)

## Similarity (according to introversion)
net1_clean <- graph_from_data_frame(d = edge1, vertices = node_clean, directed = TRUE)
sim1 <- assortativity(net1_clean, V(net1_clean)$introversion, directed=T)
```




###### Calculating measures of centrality and similarity in networks for **Tie Type 2**

```{r, message=FALSE, warning=FALSE}
edge2 <- edge_list %>% filter(Tie_Type == 2)
net2 <- graph_from_data_frame(d = edge2, vertices = node_clean, directed = TRUE)

deg2 <- degree(net2, mode="all") ## Degree
avg_deg2 <- mean(deg2)

close2 <- closeness(net2, mode="all", weights=NA) ## Closeness
avg_close2 <- mean(close2)

between2 <- betweenness(net2, directed=T, weights=NA) ## Betweenness
avg_between2 <- mean(between2)

## Similarity (according to introversion)
net2_clean <- graph_from_data_frame(d = edge2, vertices = node_clean, directed = TRUE)
sim2 <- assortativity(net2_clean, V(net2_clean)$introversion, directed=T)
```




###### Calculating measures of centrality and similarity in networks for **Tie Type 3**

```{r, message=FALSE, warning=FALSE}
edge3 <- edge_list %>% filter(Tie_Type == 3)
net3 <- graph_from_data_frame(d = edge3, vertices = node_clean, directed = TRUE)

deg3 <- degree(net3, mode="all") ## Degree
avg_deg3 <- mean(deg3)

close3 <- closeness(net3, mode="all", weights=NA) ## Closeness
avg_close3 <- mean(close3)

between3 <- betweenness(net3, directed=T, weights=NA) ## Betweenness
avg_between3 <- mean(between3)

## Similarity (according to introversion)
net3_clean <- graph_from_data_frame(d = edge3, vertices = node_clean, directed = TRUE)
sim3 <- assortativity(net3_clean, V(net3_clean)$introversion, directed=T)
```



###### Calculating measures of centrality and similarity in networks for **Tie Type 4**

```{r, message=FALSE, warning=FALSE}
edge4 <- edge_list %>% filter(Tie_Type == 4)
net4 <- graph_from_data_frame(d = edge4, vertices = node_clean, directed = TRUE)

deg4 <- degree(net4, mode="all") ## Degree
avg_deg4 <- mean(deg4)


close4 <- closeness(net4, mode="all", weights=NA) ## Closeness
avg_close4 <- mean(close4)


between4 <- betweenness(net4, directed=T, weights=NA) ## Betweenness
avg_between4 <- mean(between4)

## Similarity (according to introversion)
net4_clean <- graph_from_data_frame(d = edge4, vertices = node_clean, directed = TRUE)
sim4 <- assortativity(net4_clean, V(net4_clean)$introversion, directed=T)
```




###### Calculating measures of centrality and similarity in networks for **Tie Type 5**

```{r, message=FALSE, warning=FALSE}
edge5 <- edge_list %>% filter(Tie_Type == 5)
net5 <- graph_from_data_frame(d = edge5, vertices = node_clean, directed = TRUE)

deg5 <- degree(net5, mode="all") ## Degree
avg_deg5 <- mean(deg5)

close5 <- closeness(net5, mode="all", weights=NA) ## Closeness
avg_close5 <- mean(close5)

between5 <- betweenness(net5, directed=T, weights=NA) ## Betweenness
avg_between5 <- mean(between5)

## Similarity (according to introversion)
net5_clean <- graph_from_data_frame(d = edge5, vertices = node_clean, directed = TRUE)
sim5 <- assortativity(net5_clean, V(net5_clean)$introversion, directed=T)
```

```{r, include=FALSE}
library(kableExtra)
```

$$\\[.01in]$$


### **Measures of Centrality in Networks by Tie Type**
```{r, message=FALSE}
## Table showing measures of centrality by tie type
centrality_table <- data.frame(Tie_Type = c("Type 1", "Type 2", "Type 3", "Type 4", "Type 5"),
                               Average_Degree = c(avg_deg1, avg_deg2, avg_deg3, avg_deg4, avg_deg5),
                               Average_Closeness = c(avg_close1, avg_close2, avg_close3, avg_close4, avg_close5),
                               Average_Between = c(avg_between1, avg_between2, avg_between3, avg_between4, avg_between5))

colnames(centrality_table)[1] <- "Tie Type" 
colnames(centrality_table)[2] <- "Degree (avg.)" 
colnames(centrality_table)[3] <- "Closeness (avg.)" 
colnames(centrality_table)[4] <- "Betweenness (avg.)"

centrality_table %>% kbl() %>% kable_styling()
```







$$\\[.01in]$$


### **Similarity in Networks (in terms of *introversion*) by Tie Type**
```{r, message=FALSE}
similarity_table <- data.frame(Tie_Type = c("Type 1", "Type 2", "Type 3", "Type 4", "Type 5"),
                               Similarity = c(sim1, sim2, sim3, sim4, sim5))

colnames(similarity_table)[1] <- "Tie Type"

similarity_table %>% kbl() %>% kable_styling()
```

#### As shown above, **Tie Type 1** (i.e. having texted a person in the last 7 days) generates the *most* similar network in terms of introversion, while **Tie Type 3** (i.e. friendship) generates the *least* similar networks in terms of introversion.



