---
title: 'Question #3'
author: ""
date: ""
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::knit_hooks$set(crop = knitr::hook_pdfcrop)
```

$$\\[.01in]$$

# *Do introverts tend to be at the periphery while extraverts are in the center of the network? Motivate.*


$$\\[.01in]$$


```{r, include=FALSE}
## Set-up
library(tidyverse)
library(lubridate)
library(dplyr)
library(ggplot2)
library(sna)
library(readxl)
library(network)
library(splitstackshape)
library(igraph)
setwd("~/Desktop/BDS516")
edge_list <- read_csv("edge_list.csv")
edge_list <- edge_list %>% select(-X1)
node_list <- read_csv("node_list.csv")
node_list <- node_list %>% select(-X1)
```

```{r, results='hold', fig.align='center', fig.height=6, fig.width=7.5}
node_list2 <- node_list
node_list2$introversion[node_list2$introversion== 1] <- "Introvert"  
node_list2$introversion[node_list2$introversion== 2] <- "Ambivert"  
node_list2$introversion[node_list2$introversion== 3] <- "Extrovert"  

introvert_network <- graph_from_data_frame(d=edge_list, vertices=node_list2, directed=F)

#Plotting network
V(introvert_network)$color <- ifelse(V(introvert_network)$introversion == "Introvert", "lightblue",
                              ifelse(V(introvert_network)$introversion == "Extrovert", "darkred",
                              ifelse(V(introvert_network)$introversion == "Ambivert", "purple", "grey")))
V(introvert_network)$label <- NA

set.seed(04917)
plot(introvert_network, vertex.size = 10, vertex.label.cex = .8, edge.color = "black", 
     edge.curved = FALSE, layout=layout_with_drl, main = "Visualization of BDS 516 Social Network", font.main = 3.5)

set.seed(04917)
legend("bottomright", c("Introvert","Extrovert", "Ambivert", "NA"), pt.bg=c("lightblue","darkred","purple", "white"),
       pch=21, col="#777777", pt.cex=1.75, cex=.8, adj = c(0, 0.6))
```


##### In order to determine if extroverts are in the middle of the network and introverts are at the periphery, the ambiverts and NA are irrelevant datapoints. Therefore, this leaves three data points for extroverts and three data points for introverts. Given these six data points, it does seem to be the case that extroverts are at the center of the network and introverts are at the periphery.
















